---
title: "P8105 Homework 1"
author: "Kayla Schiffer-Kane"
date: September 23, 2023
output: 
  github_document:
    toc: true
---

# Problem 1

## Load and Explore Dataset

```{r load_data}
library(moderndive)
data("early_january_weather")
jan_df = early_january_weather
```

Below are some basic descriptors of this dataset, which provides hourly weather for airports:

* The data set has **`r nrow(jan_df)` rows** and **`r ncol(jan_df)` variables**.
* The variables in this dataset are as follows: _`r colnames(jan_df)`_.
* Of particular note, the _origin_ of the weather is _`r unique(jan_df$origin)`_ and the data is recorded for the _year_ _`r unique(jan_df$year)`_. It covers data on the _month_ of _`r unique(jan_df$month)`_ (January) up to the _`r max(jan_df$day)`_ th _day_, hence "early" January weather!
* The **mean temperature** is `r mean(jan_df$temp)`


## Data Visualization
Creating a scatter plot of `temp` (y) vs `time_hour` (x); color points using the `humid` variable (adding `color = ...` inside of `aes` in your ggplot code should help). Describe patterns that are apparent in this plot.

```{r scatter_plot, message = FALSE}
library(tidyverse)
ggplot(jan_df, aes(x = hour, y = temp, color = humid)) + geom_point()
ggsave("hour_temp.pdf", height = 4, width = 8)
```


# Problem 2

```{r data_frame}
tibble(
  vec_norm = rnorm(10),
  vec_log = vec_norm > 0,
  vec_char = c(letters[0:10])
#  vec_factor 
)

```

