---
title: "P8105 Homework 1"
author: "Kayla Schiffer-Kane"
date: September 23, 2023
output: 
  github_document:
    toc: true
---

# Problem 1

## Load and Explore Dataset


```{r load_data}
library(moderndive)
data("early_january_weather")
jan_df = early_january_weather
```

Exploring which variables are "important"/descriptive of the dataset 

```{r explore_data}
colnames(jan_df)
summary(jan_df)
?early_january_weather
```


Below are some basic descriptors of this dataset, which provides hourly weather for airports:

* The data set has **`r nrow(jan_df)` rows** and **`r ncol(jan_df)` variables**.
* The variables in this dataset are as follows: _`r colnames(jan_df)`_.
* Of particular note, the _origin_ of the weather is _`r unique(jan_df$origin)`_ and the data is recorded for the _year_ _`r unique(jan_df$year)`_. It covers data on the _month_ of _`r unique(jan_df$month)`_ (January) up to the _`r max(jan_df$day)`_ th _day_, hence "early" January weather!
* The **mean temperature** is `r mean(jan_df$temp)`
